A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-03-21 CC/writeup.Rnw
vertices need a label column

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}
\hh{XXX I've set tidy to FALSE; for some reason it's totally messing up the line width.}
<<chunk_setup, echo=FALSE>>=
opts_chunk$set(tidy = FALSE, echo=FALSE, eval = FALSE, message = FALSE, warning = FALSE,  fig.height = 8, fig.width = 8, fig.align = 'center')
@
<<readingdata>>=
 library(knitr)
 library(ggplot2) # needs to be the version with geom_net!
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements, lesmis)
 load("data/madmen.rda") # relative path should work for both of us
 email.net <- read.csv("data/email-data.csv")
 email.names <- data.frame(name = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to)))))
@

>>>>

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}
\hh{XXX I've set tidy to FALSE; for some reason it's totally messing up the line width.}
<<chunk_setup, echo=FALSE>>=
library(knitr)
opts_chunk$set(tidy = FALSE, echo=FALSE, eval = FALSE, message = FALSE, warning = FALSE,  fig.height = 8, fig.width = 8, fig.align = 'center')
@
<<readingdata>>=
 library(ggplot2) # needs to be the version with geom_net!
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements, lesmis)
 load("data/madmen.rda") # relative path should work for both of us
names(madmen$vertices)[1] <- "label"
names(blood$vertices)[1] <- "label"

 email.net <- read.csv("data/email-data.csv")
 email.names <- data.frame(label = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to)))))
